Proposed Solution

### 2016-02-09 CAV/abs.tex
make a new dir for icfp

Software failures resulting from configuration errors 
have become commonplace as modern software systems 
grow increasingly large and more complex.
The lack of language constructs in configuration files, 
such as types and grammars, 
has directed the focus of a configuration file verification 
towards building post-failure error diagnosis tools. 
In addition, the existing tools are generally language
specific, requiring the user to define at least a grammar for the language
models and explicit rules to check. 
In this paper, we propose a framework which analyzes
datasets of correct configuration files and derives rules for building a
language model from the given dataset. 
The resulting language model can be used
to verify new configuration files and detect errors in them. 
Our proposed framework is highly modular, 
does not rely on the system source code, and
can be applied to any new configuration file type with minimal user input.  
Our tool, named \app, relies on an abstract representation of language 
rules to allow for this modularity. 
\app supports learning of various rules, such as orderings,
value relations, type errors, or user definied rules
by using a probabilistic type inference stategy and
defining a small interface for the rule type.

>>>>

Software failures resulting from configuration errors 
have become commonplace as modern software systems 
grow increasingly large and more complex.
The lack of language constructs in configuration files, 
such as types and grammars, 
has directed the focus of a configuration file verification 
towards building post-failure error diagnosis tools. 
In addition, the existing tools are generally language
specific, requiring the user to define at least a grammar for the language
models and explicit rules to check. 
In this paper, we propose a framework which analyzes
datasets of correct configuration files and derives rules for building a
language model from the given dataset. 
The resulting language model can be used
to verify new configuration files and detect errors in them. 
Our proposed framework is highly modular, 
does not rely on the system source code, and
can be applied to any new configuration file type with minimal user input.  
Our tool, named \app, relies on an abstract representation of language 
rules to allow for this modularity. 
\app supports learning of various rules, such as orderings,
value relations, type errors, or user defined rules
by using a probabilistic type inference strategy and
defining a small interface for the rule type.

### 2016-02-09 CAV/design.tex
make a new dir for icfp

\begin{figure}[t] \centering
\includegraphics[width=0.8\textwidth]{figs/overview}
\caption{\app's workflow overview.}
\label{fig-overview}
\end{figure}

@@

There is actually a bit of a catch in ordering though - we are not complete over ordering rules.
This is because only our implementation does not satisfy the specification for the merge function listed above.
The problem arises from the fact the configuration files may have non-unique keywords.
Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
\begin{verbatim}
[client]
port = 3306
[mysqld]
port = 3306
\end{verbatim}
Our implementation of merge removes and conflicting rules for the running set.
By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.

>>>>

@@

There is actually a bit of a catch in ordering though - we are not complete over ordering rules.\xxx{since last code update to add context we complete again}
This is because only our implementation does not satisfy the specification for the merge function listed above.
The problem arises from the fact the configuration files may have non-unique keywords.
Therefor, in the follwoing file we will derive the valid, but conflicting rules ([client],port) and (port,[client]).
\begin{verbatim}
[client]
port = 3306
[mysqld]
port = 3306
\end{verbatim}
Our implementation of merge removes and conflicting rules for the running set.
By introducing a renaming pass in the initial parsing we may be able to solve this, but have not found a satisfactory solution yet.

### 2016-02-09 CAV/system.tex
make a new dir for icfp

{\bf {Rules Learning.}}

While a traditional classification learning machine learning approach can reduce both of these situations, there is can generally be no guarantee that all false negatives will be eliminated. Instead of building classification models over the learning set (such as an SVM), we learn the largest set of rules that all correct configuration files satisfy. In this way, \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set. The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing. Framed as the question "Is this file valid", \app is complete but not sound

>>>>

{\bf {Rule Learning.}} With every type we associate a set of templates, specific to this type. Once the input files are fully type-annotated, we generate rules that are instances of these templates. We always learn the largest set of rules that all correct configuration files satisfy. This way \app can guarantee that, over the set of rules we consider, there will be no false negatives that could have been caught with the given learning set. The only case of a false negative can be when there was no evidence of such a rule in the learning set - we cannot generate rules from nothing. 
%Framed as the question "Is this file valid", \app is complete but not sound
